---
title: "Label Statistics"
output:
  html_document:
    fig_width: 8
    fig_height: 8


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width='750px', dpi=200)
```

Import Libraries
```{r, message=FALSE}
library(Hmisc)
library(dplyr)
library(plyr)
library(xlsx)
library(reshape2)
library(tidyr)
require(ggplot2)
```


```{r}
#Clears everything (useful when not knitting and testing things in the console)
rm(list=ls())
```


#Data Information: 
The resulting contours (scores) are then normalised to the range of −1 to +1 and median filtered (with a width of 3 samples). Then, in order to attenuate the effect of a different interpretations of the scale, the normalised and filtered ratings are standardised to the average standard deviation of all anno- tators.


Load Data
```{r, echo=FALSE}
#Get Files
label_files <- list.files(path='../data/AVEC_17_Emotion_Sub-Challenge/labels/', full.names = TRUE) 

#Load Files into One Dataframe
AVEC<- read.table(label_files[1], header=F, sep = ";")
for (subject in 2:length(label_files)){
    temp_data <- read.table(label_files[subject], header=F, sep = ";")
    AVEC <- rbind(AVEC, temp_data)
}
rm(temp_data)
rm(label_files)
rm(subject)
  
#Rename Files
names(AVEC) = c("instancename", "timestamp", "arousal", "valence", "liking")

#Make Label Names File
labelnames <- c("arousal", "valence", "liking")
```


Initialize Graph Paramaters
```{r}
center_title <- theme(plot.title = element_text(hjust = 0.5))
theme =  theme(legend.position="none", panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

Histograms (Time Invariant)
```{r}
for (xvalue in labelnames) {
  print(
    ggplot(AVEC, aes_string(x=xvalue)) + geom_histogram(alpha=.6) + theme_bw() + ggtitle(xvalue) + center_title +
      xlim(-1,1)
  )
}

for (xvalue in labelnames) {
  print(
    ggplot(AVEC, aes_string(x=xvalue, fill = "instancename")) + geom_histogram() + theme_bw() + ggtitle(xvalue) + center_title +
      xlim(-1,1) + theme + facet_wrap(~instancename)
  )
}
```


Labels by Timestamp (split by participant)
```{r}
for (yvalue in labelnames) {
  xvalue = "timestamp"
  print(
    ggplot(AVEC, aes_string(x=xvalue, y=yvalue)) + geom_line() + theme_bw() + ggtitle(paste(yvalue,"by",xvalue)) + center_title +
      facet_wrap(~instancename) + theme
  )
}
```

Summary Function 
```{r, echo=FALSE, message=FALSE}
#Summary Function
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- reshape::rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}
```



#Individual Participant Label Means and Standard Deviations
```{r}

pSummary <- summarySE(AVEC, measurevar="arousal", groupvars=c("instancename"))
ggplot(pSummary, aes(x=instancename, y=arousal, colour=instancename)) +  theme_bw() +
    geom_point(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=arousal-sd, ymax=arousal+sd),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + theme


pSummary <- summarySE(AVEC, measurevar="valence", groupvars=c("instancename"))
ggplot(pSummary, aes(x=instancename, y=valence, colour=instancename)) +  theme_bw() +
    geom_point(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=valence-sd, ymax=valence+sd),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + theme

pSummary <- summarySE(AVEC, measurevar="liking", groupvars=c("instancename"))
ggplot(pSummary, aes(x=instancename, y=liking, colour=instancename)) +  theme_bw() +
    geom_point(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=liking-sd, ymax=liking+sd),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + theme
```

Relationship Between Label Names (repeats because I'm too lazy to fix the loops)
```{r}
for (yvalue in labelnames) {
  for (xvalue in labelnames) {
    if (xvalue != yvalue) {
        print(
          ggplot(AVEC, aes_string(x=xvalue, y=yvalue)) + geom_point(size=.5) + theme_bw() + ggtitle(paste(yvalue,"by",xvalue)) + center_title +
            facet_wrap(~instancename) + theme
        )
    }
  }
}
```

